### 2020-06-20 docs/LaTex/Paper.tex
Completes docs

\subsubsubsection{Arduino sketch}
In a first place, \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino}{the sketch} can be found in \cmd{src/dendro/dendro.ino} path.

By other hand, in order to this sketch takes advantage of the plugged LoRa Shield, is required to base it on the LoRaMAC-in-C library \cite{MCCI_lmic} (\cmd{arduino-lmic})\footnote{Dragino has a \href{https://github.com/dragino/arduino-lmic}{fork of this library} but has been considered less upgraded than the MCCI version, which is a fork itself from the first port of LMIC library by \href{https://github.com/matthijskooijman}{Matthijs Kooijman}.} implemented by \href{https://mcci.com/}{MCCI}, whose technical documentation can be found in \cite{MCCI_lmic_docs}. The \cmd{arduino-lmic} library is, as its description in the README.md says, a port from the IBM LoRaWAN MAC in C, but \enquote{slightly modified to run in the Arduino environment allowing using the SX1272, SX1276 transceivers and compatible modules} \cite{MCCI_lmic}.

@@

Basically the sketch is based on the \href{https://github.com/mcci-catena/arduino-lmic/blob/master/examples/ttn-abp/ttn-abp.ino}{ttn-abp example}, as the reader can see in the first comment block; that example sends a LoRaWAN valid package with the payload \enquote{Hello World!}.

>>>>

\subsubsubsection{Arduino sketch}
In a first place, \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino}{the sketch} can be found in \cmd{src/dendro/dendro.ino} path. This is the sketch that must be uploaded to arduino microcontroller. MEGA 2560 in this case.

By other hand, in order to this sketch takes advantage of the plugged LoRa Shield, is required to base it on the LoRaMAC-in-C library \cite{MCCI_lmic} (\cmd{arduino-lmic})\footnote{Dragino has a \href{https://github.com/dragino/arduino-lmic}{fork of this library} but has been considered less upgraded than the MCCI version, which is a fork itself from the first port of LMIC library by \href{https://github.com/matthijskooijman}{Matthijs Kooijman}.} implemented by \href{https://mcci.com/}{MCCI}, whose technical documentation can be found in \cite{MCCI_lmic_docs}. The \cmd{arduino-lmic} library is, as its description in the README.md says, a port from the IBM LoRaWAN MAC in C, but \enquote{slightly modified to run in the Arduino environment allowing using the SX1272, SX1276 transceivers and compatible modules} \cite{MCCI_lmic}. The original IBM LoRaWAN MAC in C library was developed for microcontrollers in general, their examples and HAL ---Hardware Abstraction Layer or rather Hardware Annotation Library--- were only for STM32 MCUs (but bare-metal, so no Arduino on top).

@@

Basically the sketch is based on the \href{https://github.com/mcci-catena/arduino-lmic/blob/master/examples/ttn-abp/ttn-abp.ino}{ttn-abp example}, as the reader can see in the first comment block; that example sends a LoRaWAN valid package with the payload \enquote{Hello World!}. Besides it uses the ABP (Activation-by-personalisation) method ---in opposition to OTAA (Over-the-air-activation) method---, depending on the used method it is necessary to include different security keys provided by The Things Network stack in the code.

As commented \href{https://github.com/mcci-catena/arduino-lmic/blob/master/examples/ttn-abp/ttn-abp.ino#L29}{lines 29 and 30} point
